Simulating spaces and stressors

### 2021-02-18 Analysis/01_Simulating_spaces_and_stressors.Rmd
updated simulation tests

---
title: "Simulating spaces and stressors"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

@@

```{r}
## Creating the trait object (2D BM)
my_trait <- make.traits(process = BM.process, n = 2)

@@

    ## Adding the legend
    if(!missing(legend)) {
        legend(x = "topleft", col = col, pch = pch, legend = legend)
    }
    ## Add the points
    points(x = data[null, trait], y = rep(0, sum(null)), col = "black", bg = col[1], pch = 21)
    points(x = data[reduction, trait], y = rep(-1, sum(reduction)), col = "black", bg = col[2], pch = 21)
}
plot.2D <- function(data, reduction, null, main, col = c("blue", "orange"), pch= 19, trait = c(1,2), xlab = "trait values", legend) {
    ## Plotting the histogram
    plot(NULL, xlim = range(trait_space[, trait[1]]), ylim = range(trait_space[, trait[2]]), main = main)
    points(trait_space[null, trait], pch = pch, col = col[1])
    points(trait_space[reduction, trait], pch = pch, col = col[2])
    ## Adding the legend
    if(!missing(legend)) {
        legend(x = "topleft", col = col, pch = pch, legend = legend)
    }
}
```

```{r}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = random_reduction, null = rep(TRUE, 200), main = "1D null mechanism", legend = c("Full distribution (200sp)", "Random reduction (100sp)"))
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")
```

@@

```{r}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D null mechanism")
```

@@

```{r}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D null mechanism")
```

@@

```{r}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D null mechanism")
```

@@

```{r}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D null mechanism")
```

>>>>

---
title: "Simulating spaces and stressors"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

@@

```{r, fig.height = 12, fig.width = 6}
## Creating the trait object (2D BM)
my_trait <- make.traits(process = BM.process, n = 2)

@@

    ## Adding the legend
    if(!missing(legend)) {
        legend(x = "topleft", col = col, pch = pch, legend = legend)
    }
    ## Add the points
    points(x = data[null, trait], y = rep(0, sum(null)), col = "black", bg = col[1], pch = 21)
    points(x = data[reduction, trait], y = rep(-plot_height/50, sum(reduction)), col = "black", bg = col[2], pch = 21)
}
plot.2D <- function(data, reduction, null, main, col = c("blue", "orange"), pch= 19, trait = c(1,2), xlab = "trait values", legend) {
    ## Plotting the histogram
    plot(NULL, xlim = range(trait_space[, trait[1]]), ylim = range(trait_space[, trait[2]]), main = main)
    points(trait_space[null, trait], pch = pch, col = col[1])
    points(trait_space[reduction, trait], pch = pch, col = col[2])
    ## Adding the legend
    if(!missing(legend)) {
        legend(x = "topleft", col = col, pch = pch, legend = legend)
    }
}
```

```{r, fig.height = 12, fig.width = 6}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = random_reduction, null = rep(TRUE, 200), main = "1D null mechanism", legend = c("Full distribution (200sp)", "Random reduction (100sp)"))
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")
```

@@

```{r, fig.height = 12, fig.width = 6}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")
```

@@

```{r, fig.height = 12, fig.width = 6}

## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D excluding mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D excluding mechanism")
```

@@

```{r, fig.height = 12, fig.width = 6}

## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")
```

@@

```{r, fig.height = 12, fig.width = 6}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")
```
